### 2023-04-24 Rmd/Paper 03 short term forecast analysis.Rmd
short term forecast paper

# Libraries
library(rmarkdown) # creating markdown documents
library(tidyverse) # combined package of dplyr, tidyr, ggplot, readr, purrr and tibble
library(reshape2)  # reshaping data; e.g. dcast
library(ggthemes)  # for themes
library(pander)    # for print tables
library(readxl)    # read excel files
library(cowplot)   # multiplots
library(directlabels)  # label graphs
library(RColorBrewer) # colours
library(lubridate)

# Load utils code
source("../../prf/r/my utils.r")

@@

# Load dataset
load(file=paste(dropboxdir, "/rdata/iAssess.RData",sep=""))
load(file=paste(dropboxdir, "/rdata/iAdvice.RData",sep=""))

@@

# stock=c("spr-nsea","spr.27.3a4"); firstassessyear=2016;lastassessyear=2019;firstyear=2000;lastyear=2020; include.benchmark==TRUE
# stock=c("mac-nea"); firstassessyear=2016;lastassessyear=2019;firstyear=2000;lastyear=2020; include.benchmark=TRUE; plot=c("stocksize","fishingpressure","recruitment")

# d %>% filter(stockkeylabelold == "mac-nea", assessmentyear == 2019) %>% View()
# unique(iAssess$purpose)

# Function to plot historical assessments
plot_history <- function(stock,firstassessyear,lastassessyear, firstyear, lastyear, include.benchmark = FALSE, 
                         plot=c("stocksize","fishingpressure")) {

  d <-
    iAssess %>% 
    ungroup() %>%

    {if (include.benchmark == TRUE) {
      filter(., purpose %in% c("advice","benchmark", "interbenchmark", "bench"))
    } else {
      filter(., purpose %in% c("advice")) 
    }} %>%

    filter(stockkeylabelold %in% stock | stockkeylabel %in% stock) %>%

    filter(assessmentyear   %in% c(firstassessyear:lastassessyear), 
           year             %in% firstyear:lastyear) %>%

    mutate(tyear     = substr(as.character(assessmentyear), 3,4)) %>%

    #set type
    mutate(
      type = ifelse(assessmentyear == lastassessyear & purpose == "advice"       , "last"      , NA),
      type = ifelse(assessmentyear == lastassessyear & grepl("bench",purpose),  "last_bench", type),  
      type = ifelse(assessmentyear != lastassessyear & purpose == "advice"       , "advice"    , type),
      type = ifelse(assessmentyear != lastassessyear & grepl("bench",purpose),  "benchmark" , type),
      type = ifelse(assessmentyear != lastassessyear & grepl("replaced",purpose) , "replaced"  , type),
      type = ifelse(is.na(type), "other", type)) %>%

    # set group
    mutate(group = paste0(tyear, type)) %>%

    select(assessmentyear, tyear, year, stockkey, stockkeylabel, stockkeylabelold, stockkeylabelnew,
           type, group, source,
           lowrecruitment, recruitment, highrecruitment, 
           lowfishingpressure, fishingpressure, highfishingpressure, 
           lowstocksize, stocksize, highstocksize) %>%
    data.frame()

  # find out what is the last assessment
  last <- filter(d, assessmentyear == lastassessyear) %>% distinct(type) %>% as.character()

  # plot stocksize
  stocksize <-
    d %>% 
    filter(!is.na(stocksize)) %>%

    ggplot(aes(year,stocksize, group=group)) +

    theme_publication() +

    theme(legend.title=element_blank(),
          axis.text.x = element_text(angle = 0, vjust = 0.5, size=9),
          axis.text.y = element_text(size=9),
          plot.title  = element_text(size=10), 
          plot.margin = margin(2, 2, 2, 2, "mm"),
          # strip.background = element_blank(),
          legend.position = "null") +

    geom_ribbon(data=filter(d, type==last), 
                aes(x=year, ymin=lowstocksize, ymax=highstocksize, fill=type), 
                alpha=0.2) +
    geom_line(aes(colour = type, size=type, linetype=type) ) +

    geom_dl(aes(label  = tyear, colour = type), method = list(dl.combine("last.points"), cex = 0.8)) +

    geom_hline(data=filter(iAdvice, stockkeylabelold %in% stock | stockkeylabel %in% stock, assessmentyear == lastassessyear),
               aes(x=assessmentyear, yintercept=blim, label="blim", vjust=-1), 
               colour="red", inherit.aes=FALSE) +
    geom_text (data=filter(iAdvice, stockkeylabelold %in% stock | stockkeylabel %in% stock, assessmentyear == lastassessyear),
               aes( firstyear, blim, label = "blim", vjust = -0.3, hjust = 0),
               colour="red", inherit.aes = FALSE) +

    geom_hline(data=filter(iAdvice, stockkeylabelold %in% stock | stockkeylabel %in% stock, assessmentyear == lastassessyear),
               aes(x=assessmentyear, yintercept=msybtrigger), 
               colour="red", linetype="dashed", inherit.aes=FALSE) +
    geom_text (data=filter(iAdvice, stockkeylabelold %in% stock | stockkeylabel %in% stock, assessmentyear == lastassessyear),
               aes( firstyear, msybtrigger, label = "msy btrigger", vjust = -0.3, hjust = 0),
               colour="red", inherit.aes=FALSE) +

    scale_colour_manual  (values=c(last ="red",last_bench="blue",advice="black",benchmark="blue",replaced="gray40",other="gray80")) +
    scale_fill_manual    (values=c(last = "red",last_bench="blue",advice="black",benchmark="blue",replaced="gray40",other="gray80")) +
    scale_linetype_manual(values=c(last="solid",last_bench="solid",advice="solid",benchmark="solid",replaced="solid",other="solid")) +
    scale_size_manual    (values=c(last= 1.2,last_bench=1.2,advice=0.8,benchmark=0.8,replaced=0.8,other=0.8)) +

    expand_limits(y = 0) +
    xlim(firstyear,lastyear) +
    labs(x = NULL, y = NULL , title = "stocksize")

  # fishingpressure
  fishingpressure <-
    d %>% 
    filter(!is.na(fishingpressure)) %>%

    ggplot(aes(year,fishingpressure, group=group)) +

    theme_publication() +
    theme(legend.title=element_blank(),
          axis.text.x = element_text(angle = 0, vjust = 0.5, size=9),
          axis.text.y = element_text(size=9),
          plot.title  = element_text(size=10), 
          plot.margin = margin(2, 2, 2, 2, "mm"),
          # strip.background = element_blank(),
          legend.position = "null") +

    geom_ribbon(data=filter(d, type==last), 
                aes(x=year, ymin=lowfishingpressure, ymax=highfishingpressure, fill=type), 
                alpha=0.2) +
    geom_line(aes(colour = type, size=type, linetype=type) ) +

    geom_dl(aes(label  = tyear, colour = type), method = list(dl.combine("last.points"), cex = 0.8)) +

    geom_hline(data=filter(iAdvice, stockkeylabelold %in% stock | stockkeylabel %in% stock, assessmentyear == lastassessyear),
               aes(x=assessmentyear, yintercept=fmsy), 
               colour="red", linetype="dashed", inherit.aes=FALSE) +
    geom_text (data=filter(iAdvice, stockkeylabelold %in% stock | stockkeylabel %in% stock, assessmentyear == lastassessyear),
               aes( firstyear, fmsy, label = "fmsy", vjust = -0.3, hjust = 0),
               colour="red", inherit.aes=FALSE) +

    scale_colour_manual  (values=c(last ="red",last_bench="blue",advice="black",benchmark="blue",replaced="gray40",other="gray80")) +
    scale_fill_manual    (values=c(last = "red",last_bench="blue",advice="black",benchmark="blue",replaced="gray40",other="gray80")) +
    scale_linetype_manual(values=c(last="solid",last_bench="solid",advice="solid",benchmark="solid",replaced="solid",other="solid")) +
    scale_size_manual    (values=c(last= 1.2,last_bench=1.2,advice=0.8,benchmark=0.8,replaced=0.8,other=0.8)) +

    expand_limits(y = 0) +
    xlim(firstyear,lastyear) +
    labs(x = NULL, y = NULL , title = "fishingpressure")

  # Recruitment
  recruitment <-
    d %>% 
    filter(!is.na(recruitment)) %>%

    ggplot(aes(year,recruitment, group=group)) +

    theme_publication() +
    theme(legend.title=element_blank(),
          axis.text.x = element_text(angle = 0, vjust = 0.5, size=9),
          axis.text.y = element_text(size=9),
          plot.title  = element_text(size=10), 
          plot.margin = margin(2, 2, 2, 2, "mm"),
          # strip.background = element_blank(),
          legend.position = "null") +

    geom_ribbon(data=filter(d, type==last), 
                aes(x=year, ymin=lowrecruitment, ymax=highrecruitment, fill=type), 
                alpha=0.2) +
    geom_line(aes(colour = type, size=type, linetype=type) ) +

    geom_dl(aes(label  = tyear, colour = type), method = list(dl.combine("last.points"), cex = 0.8)) +

    scale_colour_manual  (values=c(last ="red",last_bench="blue",advice="black",benchmark="blue",replaced="gray40",other="gray80")) +
    scale_fill_manual    (values=c(last = "red",last_bench="blue",advice="black",benchmark="blue",replaced="gray40",other="gray80")) +
    scale_linetype_manual(values=c(last="solid",last_bench="solid",advice="solid",benchmark="solid",replaced="solid",other="solid")) +
    scale_size_manual    (values=c(last= 1.2,last_bench=1.2,advice=0.8,benchmark=0.8,replaced=0.8,other=0.8)) +

    expand_limits(y = 0) +
    xlim(firstyear,lastyear) +
    labs(x = NULL, y = NULL , title = "Recruitment")

    if (length(plot) == 1) {
      if ("stocksize" %in% plot ) print(stocksize)
      if ("fishingpressure" %in% plot ) print(fishingpressure)
      if ("recruitment" %in% plot ) print(recruitment)

    } else if (length(plot) == 2) {

      if ("stocksize" %in% plot & "fishingpressure" %in% plot) plot_grid(stocksize, fishingpressure,  ncol=2, align = 'hv') 
      if ("stocksize" %in% plot & "recruitment" %in% plot) plot_grid(stocksize, recruitment,  ncol=2, align = 'hv') 
      if ("recruitment" %in% plot & "fishingpressure" %in% plot) plot_grid(fishingpressure, recruitment,  ncol=2, align = 'hv')

    } else if (length(plot) == 3) {
        plot_grid(stocksize, fishingpressure,  recruitment, ncol=length(plot), align = 'hv') 
    }

  } # End of plot_history function

# plot_history(stock=s,firstassessyear=fay,lastassessyear=lay, firstyear=fy, lastyear=ly, include.benchmark = TRUE,               plot = c("stocksize", "fishingpressure", "recruitment"), include.benchmark = TRUE)

# firstadviceyear <- 2016; lastadviceyear  <- 2020; stock<-c("spr-nsea","spr.27.3a4"); include.replaced <- TRUE
# firstadviceyear <- 2016; lastadviceyear  <- 2020; stock<-c("mac-nea"); include.replaced <- TRUE

# Function to plot advice overviews
table_advice <- function(stock,firstadviceyear,lastadviceyear, include.replaced=FALSE) {

  d <-
    iAdvice %>%

    filter(stockkeylabelold %in% stock | stockkeylabel %in% stock) %>%

    filter(tacyear %in% firstadviceyear:lastadviceyear) %>%

    {if (include.replaced == TRUE) {
      filter(., purpose %in% c("advice","replaced"))
    } else {
      filter(., purpose %in% c("advice")) 
    }} %>%

    mutate(advicebasis= substr(advicebasis,1,25),

           advice     = ifelse(!is.na(advisedcatchmax), advisedcatchmax, advisedlandingsmax),
           advicemax  = ifelse(!is.na(advisedcatchmax), advisedcatchmax, advisedlandingsmax),
           advicetype = ifelse(!is.na(advisedcatchmax), "catch", "landings"),

           tac        = ifelse(!is.na(tac), tac, tal),
           tactype    = ifelse(!is.na(tac), "catch", "landings"),

           catch      = ifelse(!is.na(catches), catches, NA),
           catchtype  = ifelse(!is.na(catches), "catches", ""),

           catchtype  = ifelse(!is.na(landings) & is.na(catch), "landings", catchtype),
           catch      = ifelse(!is.na(landings) & is.na(catch), landings, catch),

           catchtype  = ifelse(!is.na(officiallandings) & is.na(catch), "officiallandings", catchtype),
           catch      = ifelse(!is.na(officiallandings) & is.na(catch), officiallandings, catch),

           adv_c      = 100 * (advicemax / lag(advicemax, n=1) - 1),
           tac_c      = 100 * (tac /lag(tac, n=1) - 1),
           cat_c       = 100 * (catch / lag(catch, n=1) -1)
           ) %>%

    select(stockkeylabel, tacyear, advicebasis, purpose, advice, fadvmax, advicemax, tac, catch, 
           adv_c, tac_c, cat_c,
           advicetype, tactype, catchtype)

  d %>% 
  select("stockkeylabel", "tacyear", "advicebasis", "purpose", "fadvmax", "advicemax", "tac", "catch") %>%
  arrange(tacyear, desc(purpose)) %>% 
  pandoc.table(., 
               style        = "simple",
               split.tables = 200, 
               justify      = "right",
               missing      =" ",
               big.mark     = '', 
               round        = c(0,0,0,2,2,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))
}

# table_advice(stock=s,firstadviceyear=fay+1,lastadviceyear=lay+1, include.replaced = TRUE)

@@

```{r, echo=FALSE, fig.asp=0.45, fig.align="center", message=FALSE, warning=FALSE}

## North Sea sole

s   <- "sol-nsea"

cat(filter(iAdvice, stockkeylabelold == s, assessmentyear == lay)$stocklongname)

plot_history(stock=s,firstassessyear=fay,lastassessyear=lay, firstyear=fy, lastyear=ly, include.benchmark = TRUE,               plot = c("stocksize", "fishingpressure", "recruitment"))

table_advice(stock=s,firstadviceyear=fay+1,lastadviceyear=lay+1, include.replaced=TRUE)

d1 <-
  iAdvice %>% 
  filter(stockkeylabelold == s) %>% 
  filter(adviceonstock) %>% 
  filter(tacyear >= fy, tacyear <= ly) %>% 
  dplyr::select(stockkeylabel, stockkeylabelold, assessmentyear, year=tacyear, f=fset, ssb=ssbset) %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

d2 <-
  iAssess %>% 
  filter(stockkeylabelold==s) %>% 
  # filter(assessmentyear == max(assessmentyear)) %>% 
  filter(year >= fy, year <= ly) %>% 
  dplyr::select(stockkeylabel, stockkeylabelold, assessmentyear, year, ssb=stocksize, f=fishingpressure) %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

d2 %>% 
  ggplot(aes(x=year, y=data)) +
  theme_bw() +
  geom_line(aes(colour=as.character(assessmentyear), group=assessmentyear)) +
  geom_point(data=d1, aes(colour=as.character(assessmentyear))) +
  labs(title=s) +
  expand_limits(y=0) +
  facet_wrap(~variable, scales="free_y")

d2 %>% 
  filter(variable=="f") %>%

  ggplot(aes(x=year, y=data)) +
  theme_bw() +
  theme(legend.position="none") +
  geom_line(aes(colour=as.character(assessmentyear), group=assessmentyear)) +
  geom_point(data=filter(d1,
                         variable=="f"), 
             aes(colour=as.character(assessmentyear))) +
  labs(title=s) +
  expand_limits(y=0) +
  facet_wrap(~assessmentyear, scales="free_y")

@@

Stock size above MSY Btrigger, fishing mortality around Fmsy. Advice according to the EU multiannual plan (MAP) for the North Sea.

[sol.27.4.pdf](http://www.ices.dk/sites/pub/Publication%20Reports/Advice/2019/2019/sol.27.4.pdf)

# More information

Please refer to the [ICES website](http://www.ices.dk/community/advisory-process/Pages/Latest-advice.aspx) for an overview of all advice documents.

>>>>

# Libraries
library(rmarkdown) # creating markdown documents
library(tidyverse) # combined package of dplyr, tidyr, ggplot, readr, purrr and tibble
library(reshape2)  # reshaping data; e.g. dcast
library(ggthemes)  # for themes
library(pander)    # for print tables
library(readxl)    # read excel files
library(cowplot)   # multiplots
library(directlabels)  # label graphs
library(RColorBrewer) # colours
library(lubridate)
library(ggrepel)
library(patchwork)

# Load utils code
source("../../prf/r/my utils.r")
source("../r/iAssess functions.r")

@@

mystocks <- c("her-47d3", "whb-comb", "mac-nea", "hom-west", 
              "ple-nsea", "cod-nsea", "sol-nsea","had-nsea")

demstocks <- c("ple-nsea", "cod-nsea", "sol-nsea","had-nsea")
pelstocks <- c("her-47d3", "whb-comb", "mac-nea", "hom-west")

# Load dataset
iAssess <-
  loadRData(file=paste(dropboxdir, "/rdata/iAssess.RData",sep="")) %>% 
  mutate(stockkeylabelold = ifelse(stockkeylabelold=="ple-nsea2", 
                                   "ple-nsea", 
                                   stockkeylabelold)) %>% 
  mutate(stockkeylabelold = ifelse(stockkeylabelold %in% c("had-nsea","had-34","had-346a"),
                                   "had-nsea",
                                   stockkeylabelold)) %>% 
  mutate(stockkeylabelold = ifelse(stockkeylabelold %in% c("cod-nsea","cod-347d"),
                                   "cod-nsea",
                                   stockkeylabelold)) %>% 
  filter(stockkeylabelold %in% mystocks)

# iAdvice %>% ungroup() %>% arrange(stockkeylabelold) %>% distinct(stockkeylabelold) %>% View()

iAdvice <-
  loadRData(file=paste(dropboxdir, "/rdata/iAdvice.RData",sep="")) %>% 
  mutate(stockkeylabelold = ifelse(stockkeylabelold=="ple-nsea2", 
                                   "ple-nsea", 
                                   stockkeylabelold)) %>% 
  mutate(stockkeylabelold = ifelse(stockkeylabelold %in% c("had-nsea","had-34","had-346a"),
                                   "had-nsea",
                                   stockkeylabelold)) %>% 
  mutate(stockkeylabelold = ifelse(stockkeylabelold %in% c("cod-nsea","cod-347d"),
                                   "cod-nsea",
                                   stockkeylabelold)) %>% 
  filter(stockkeylabelold %in% mystocks)

# iAdvice %>% ungroup() %>% distinct(stockkeylabelold) %>% filter(grepl("had-",stockkeylabelold)) %>% View()

@@

myColors                <- RColorBrewer::brewer.pal(12, "Paired")[c(2:4,6,8,10)]
names(myColors)         <- c("1990", "2000", "2010", "2020", "2022")

@@

**Demersal stocks**

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

## Demersal

# advice
d1 <-
  iAdvice %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(adviceonstock) %>%
  filter(tacyear >= fy, tacyear <= ly) %>%
  dplyr::select(stockkeylabelold, year=tacyear, 
                f=fset, ssb=ssbset) %>%
  mutate(decade = as.character(10 * floor(year/10))) %>% 
  mutate(yr = stringr::str_pad(ifelse(year >=2000, year-2000, year-1900), 
                               width=2, pad="0")) %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f) %>% 
  mutate(variable = factor(variable, levels=c("ssb","f","rec")))

# assess
d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(purpose=="advice") %>% 
  # filter(assessmentyear == max(assessmentyear)) %>%
  filter(year >= fy, year <= ly) %>%
  dplyr::select(stockkeylabelold, assessmentyear, year, 
                ssb=stocksize, f=fishingpressure, rec=recruitment) %>%
  mutate(decade = as.character(10 * floor(assessmentyear/10))) %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:rec) %>% 
  mutate(variable = factor(variable, levels=c("ssb","f","rec")))

i <- 1
for (i in 1:length(demstocks)) {

  assign(paste0("p",i),
         d2 %>% 
           filter(stockkeylabelold == demstocks[[i]]) %>%

           ggplot(aes(x=year, y=data, group=assessmentyear)) +
           theme_publication() +
           geom_line(aes(colour=decade)) +
           geom_point(data=filter(d1, stockkeylabelold == demstocks[[i]]), 
                      aes(x=year, y=data, colour=decade),
                      inherit.aes=FALSE) +
           ggrepel::geom_text_repel(
                      data=filter(d1, stockkeylabelold == demstocks[[i]]),
                      aes(x=year, y=data, colour=decade, label=yr),
                      inherit.aes=FALSE) +
           expand_limits(y=0) +
           scale_colour_manual(values=myColors) +
           labs(x="",y="", title=demstocks[[i]]) +
           facet_wrap(~variable, scales="free_y")
         )
}

p1 + p2 + p3 + p4 + plot_layout(ncol = 1, guides="collect") &
  theme(legend.position='bottom')

@@

\newpage

**Pelagic stocks**

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

## Pelagic

# advice
d1 <-
  iAdvice %>%
  filter(stockkeylabelold %in% pelstocks) %>%
  filter(adviceonstock) %>%
  filter(tacyear >= fy, tacyear <= ly) %>%
  dplyr::select(stockkeylabelold, year=tacyear, 
                f=fset, ssb=ssbset) %>%
  mutate(decade = as.character(10 * floor(year/10))) %>% 
  mutate(yr = stringr::str_pad(ifelse(year >=2000, year-2000, year-1900), 
                               width=2, pad="0")) %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f) %>% 
  mutate(variable = factor(variable, levels=c("ssb","f","rec")))

# assess
d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% pelstocks) %>%
  filter(purpose=="advice") %>% 
  # filter(assessmentyear == max(assessmentyear)) %>%
  filter(year >= fy, year <= ly) %>%
  dplyr::select(stockkeylabelold, assessmentyear, year, 
                ssb=stocksize, f=fishingpressure, rec=recruitment) %>%
  mutate(decade = as.character(10 * floor(assessmentyear/10))) %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:rec) %>% 
  mutate(variable = factor(variable, levels=c("ssb","f","rec")))

i <- 1
for (i in 1:length(pelstocks)) {

  assign(paste0("p",i),
         d2 %>% 
           filter(stockkeylabelold == pelstocks[[i]]) %>%

           ggplot(aes(x=year, y=data, group=assessmentyear)) +
           theme_publication() +
           geom_line(aes(colour=decade)) +
           geom_point(data=filter(d1, stockkeylabelold == pelstocks[[i]]), 
                      aes(x=year, y=data, colour=decade),
                      inherit.aes=FALSE) +
           ggrepel::geom_text_repel(
                      data=filter(d1, stockkeylabelold == pelstocks[[i]]),
                      aes(x=year, y=data, colour=decade, label=yr),
                      inherit.aes=FALSE) +
           scale_colour_manual(values=myColors) +
           expand_limits(y=0) +
           labs(x="",y="", title=demstocks[[i]]) +
           facet_wrap(~variable, scales="free_y")
         )
}

p1 + p2 + p3 + p4 + plot_layout(ncol = 1, guides="collect") &
  theme(legend.position='bottom')

\newpage

**Demersal F**

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

# plot of F against Fset and SSB against SSBset for multiple assessments

mytype    <- "Demersal"
myvar     <- "f"

d1 <-
  iAdvice %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(adviceonstock) %>%
  filter(tacyear >= fay, tacyear <= lay) %>%
  dplyr::select(stockkeylabelold, year=tacyear, f=fset, ssb=ssbset) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% c(2000, 2010, 2020, 2022)) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

t <-
  d2 %>% 
  left_join(d1, by=c("stockkeylabelold", "year", "variable")) %>% 
  rename(
    assess=data.x,
    forecast=data.y
  ) %>% 
  drop_na(forecast) %>% 
  mutate(decade = as.character(10 * floor(year / 10))) %>% 
  mutate(yr = stringr::str_pad(ifelse(year >=2000, year-2000, year-1900), width=2, pad="0"))

# maxssb<- t %>% filter(variable=="ssb") %>% ungroup() %>% 
#   summarise(maxssb=max(assess, forecast, na.rm=TRUE)) %>% 
#   as.numeric()

i <- 1
for (i in 1:length(demstocks)) {

  max  <- t %>% 
    filter(variable==myvar) %>% 
    filter(stockkeylabelold == demstocks[[i]]) %>% 
    ungroup() %>%
    summarise(max=max(assess, forecast, na.rm=TRUE)) %>%
    as.numeric()

  assign(paste0("p",i),
         t %>% 
           filter(variable == myvar) %>% 
           filter(stockkeylabelold == demstocks[[i]]) %>%

           ggplot(aes(x=assess, y=forecast)) +
           theme_publication() +
           geom_point(aes(colour=decade)) +
           ggrepel::geom_text_repel(aes(colour=decade, label=yr)) +
           scale_colour_manual(values=myColors) +
           geom_abline(slope=1, intercept=0, linetype="dashed", linewidth=0.5) +
           scale_x_continuous(limits=c(0,max)) +
           scale_y_continuous(limits=c(0,max)) +
           facet_grid(stockkeylabelold~source)
         )
}

p1 + p2 + p3 + p4 + plot_layout(ncol = 1, guides="collect") &
  theme(legend.position='bottom')

\newpage

**Demersal SSB**

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

# plot of F against Fset and SSB against SSBset for multiple assessments

mytype    <- "Demersal"
myvar     <- "ssb"

d1 <-
  iAdvice %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(adviceonstock) %>%
  filter(tacyear >= fay, tacyear <= lay) %>%
  dplyr::select(stockkeylabelold, year=tacyear, f=fset, ssb=ssbset) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% demstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% c(2000, 2010, 2020, 2022)) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

t <-
  d2 %>% 
  left_join(d1, by=c("stockkeylabelold", "year", "variable")) %>% 
  rename(
    assess=data.x,
    forecast=data.y
  ) %>% 
  drop_na(forecast) %>% 
  mutate(decade = as.character(10 * floor(year / 10))) %>% 
  mutate(yr = stringr::str_pad(ifelse(year >=2000, year-2000, year-1900), width=2, pad="0"))

# maxssb<- t %>% filter(variable=="ssb") %>% ungroup() %>% 
#   summarise(maxssb=max(assess, forecast, na.rm=TRUE)) %>% 
#   as.numeric()

i <- 1
for (i in 1:length(demstocks)) {

  max  <- t %>% 
    filter(variable==myvar) %>% 
    filter(stockkeylabelold == demstocks[[i]]) %>% 
    ungroup() %>%
    summarise(max=max(assess, forecast, na.rm=TRUE)) %>%
    as.numeric()

  assign(paste0("p",i),
         t %>% 
           filter(variable == myvar) %>% 
           filter(stockkeylabelold == demstocks[[i]]) %>%

           ggplot(aes(x=assess, y=forecast)) +
           theme_publication() +
           geom_point(aes(colour=decade)) +
           ggrepel::geom_text_repel(aes(colour=decade, label=yr)) +
           scale_colour_manual(values=myColors) +
           geom_abline(slope=1, intercept=0, linetype="dashed", linewidth=0.5) +
           scale_x_continuous(limits=c(0,max)) +
           scale_y_continuous(limits=c(0,max)) +
           facet_grid(stockkeylabelold~source)
         )
}

p1 + p2 + p3 + p4 + plot_layout(ncol = 1, guides="collect") &
  theme(legend.position='bottom')

\newpage

**Pelagic F**

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

# plot of F against Fset and SSB against SSBset for multiple assessments

mytype    <- "Pelagic"
myvar     <- "f"

d1 <-
  iAdvice %>%
  filter(stockkeylabelold %in% pelstocks) %>%
  filter(adviceonstock) %>%
  filter(tacyear >= fay, tacyear <= lay) %>%
  dplyr::select(stockkeylabelold, year=tacyear, f=fset, ssb=ssbset) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% pelstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% c(2000, 2010, 2020, 2022)) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

t <-
  d2 %>% 
  left_join(d1, by=c("stockkeylabelold", "year", "variable")) %>% 
  rename(
    assess=data.x,
    forecast=data.y
  ) %>% 
  drop_na(forecast) %>% 
  mutate(decade = as.character(10 * floor(year / 10))) %>% 
  mutate(yr = stringr::str_pad(ifelse(year >=2000, year-2000, year-1900), width=2, pad="0"))

# maxssb<- t %>% filter(variable=="ssb") %>% ungroup() %>% 
#   summarise(maxssb=max(assess, forecast, na.rm=TRUE)) %>% 
#   as.numeric()

i <- 1
for (i in 1:length(pelstocks)) {

  max  <- t %>% 
    filter(variable==myvar) %>% 
    filter(stockkeylabelold == pelstocks[[i]]) %>% 
    ungroup() %>%
    summarise(max=max(assess, forecast, na.rm=TRUE)) %>%
    as.numeric()

  assign(paste0("p",i),
         t %>% 
           filter(variable == myvar) %>% 
           filter(stockkeylabelold == pelstocks[[i]]) %>%

           ggplot(aes(x=assess, y=forecast)) +
           theme_publication() +
           geom_point(aes(colour=decade)) +
           ggrepel::geom_text_repel(aes(colour=decade, label=yr)) +
           scale_colour_manual(values=myColors) +
           geom_abline(slope=1, intercept=0, linetype="dashed", linewidth=0.5) +
           scale_x_continuous(limits=c(0,max)) +
           scale_y_continuous(limits=c(0,max)) +
           facet_grid(stockkeylabelold~source)
         )
}

p1 + p2 + p3 + p4 + plot_layout(ncol = 1, guides="collect") &
  theme(legend.position='bottom')

\newpage

**Pelagic SSB**

```{r, echo=FALSE, fig.asp=1.2, fig.align="center", message=FALSE, warning=FALSE}

# plot of F against Fset and SSB against SSBset for multiple assessments

mytype    <- "Pelagic"
myvar     <- "ssb"

d1 <-
  iAdvice %>%
  filter(stockkeylabelold %in% pelstocks) %>%
  filter(adviceonstock) %>%
  filter(tacyear >= fay, tacyear <= lay) %>%
  dplyr::select(stockkeylabelold, year=tacyear, f=fset, ssb=ssbset) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

d2 <-
  iAssess %>%
  filter(stockkeylabelold %in% pelstocks) %>%
  filter(purpose=="advice") %>% 
  filter(assessmentyear %in% c(2000, 2010, 2020, 2022)) %>% 
  filter(year >= fay, year <= lay) %>%
  mutate(source=paste0("assess", assessmentyear)) %>% 
  dplyr::select(stockkeylabelold, year, ssb=stocksize, f=fishingpressure, source) %>%
  tidyr::pivot_longer(names_to = "variable", values_to = "data", ssb:f)

t <-
  d2 %>% 
  left_join(d1, by=c("stockkeylabelold", "year", "variable")) %>% 
  rename(
    assess=data.x,
    forecast=data.y
  ) %>% 
  drop_na(forecast) %>% 
  mutate(decade = as.character(10 * floor(year / 10))) %>% 
  mutate(yr = stringr::str_pad(ifelse(year >=2000, year-2000, year-1900), width=2, pad="0"))

# maxssb<- t %>% filter(variable=="ssb") %>% ungroup() %>% 
#   summarise(maxssb=max(assess, forecast, na.rm=TRUE)) %>% 
#   as.numeric()

i <- 1
for (i in 1:length(pelstocks)) {

  max  <- t %>% 
    filter(variable==myvar) %>% 
    filter(stockkeylabelold == pelstocks[[i]]) %>% 
    ungroup() %>%
    summarise(max=max(assess, forecast, na.rm=TRUE)) %>%
    as.numeric()

  assign(paste0("p",i),
         t %>% 
           filter(variable == myvar) %>% 
           filter(stockkeylabelold == pelstocks[[i]]) %>%

           ggplot(aes(x=assess, y=forecast)) +
           theme_publication() +
           geom_point(aes(colour=decade)) +
           ggrepel::geom_text_repel(aes(colour=decade, label=yr)) +
           scale_colour_manual(values=myColors) +
           geom_abline(slope=1, intercept=0, linetype="dashed", linewidth=0.5) +
           scale_x_continuous(limits=c(0,max)) +
           scale_y_continuous(limits=c(0,max)) +
           facet_grid(stockkeylabelold~source)
         )
}

p1 + p2 + p3 + p4 + plot_layout(ncol = 1, guides="collect") &
  theme(legend.position='bottom')
